NumPy---Array Computation for Python

### 2019-12-17 paper.tex
NEW: Start on a new dtypes section

We are busy overhauling the datatype system to make it consistent (aligned with
expectations), to simplify the creation of custom dtypes, and to enable much
requested features such as units.  The new implementation should be simpler and
more cleanly implemented.

>>>>

The meaning of each element within a NumPy array is described by its datatype
(dtype). NumPy arrays can hold all common numerical datatypes, string, datetimes
and generic Python objects, each of these is identified by a dtype.
We are busy overhauling the datatype system to make it consistent (aligned with
expectations), to simplify the creation of custom dtypes.
While numerical dtypes make the foundation for most users, there are
a multitude of use cases which cannot prosper due to current limitations.
These use cases include datatypes with physical units\cite{astropy,Goldbaum2018,pint},
% pyadolc may be a bit too small a project, so may want to remove/replace with an other example.
geometrical objects\cite{pygeos}, automatic differentiation\cite{pyadolc}, and many more.
Projects addressing these exist, each struggles with current
limitations.  % TODO: I may need citations, we could link github issues.

While it is currently possible to define custom dtypes within NumPy, many of the
use cases above cannot be solved using this system.
This is evidenced also by code within NumPy which would require changes
in many places to add such dtypes, even when adding them within NumPy itself.
The new implementation will be simpler and more cleanly implemented in
this regard.
Custom dtypes and the basic dtypes included within NumPy will be implemented
and behave identically as much as possible.
At the same time redesigning the API will make NumPy dtypes more flexible to grow
to future needs should they arise.

As a further step, to make dtypes more accessible and allow a faster adoption of
custom dtypes within the community, we plan to create a Python API to
define such custom dtypes.
